\PassOptionsToPackage{unicode,hidelinks}{hyperref}
\makeatletter
\providecommand{\AtBeginEnvironment}[2]{\AddToHook{env/#1/before}{#2}}
\providecommand{\AtEndEnvironment}[2]{\AddToHook{env/#1/after}{#2}}
\providecommand{\BeforeBeginEnvironment}[2]{}
\providecommand{\AfterEndEnvironment}[2]{}
\makeatother

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[scale=0.85]{geometry}

\name{Jane}{Doe}
\title{Data Scientist --- \textasciitilde 2 Years of Impactful Experience}
\address{}{Springfield, Country}
\phone[mobile]{+00 123 456 7890}
\email{jane.doe@example.com}
\social[linkedin]{janedoe-ds}
\social[github]{janedoe}

\begin{document}
\makecvtitle

\section{Summary}
\cvitem{}{
Data Scientist with just under 2 years of hands-on experience delivering production-level ML solutions. Expert in forecasting, automation, and dashboarding---enhanced forecast accuracy by 15\%, reduced reporting time by 10 hrs/week, and boosted customer campaign engagement by 7\%. Communicates across teams to align technical insights with strategic goals.}

\section{Skills}
\cvitem{Core}{Python, SQL, pandas, scikit-learn, PyTorch}
\cvitem{Data Tools}{Docker, Data Visualization (Tableau/Power BI), Git, Jupyter}
\cvitem{Supplementary}{R, Bash, \LaTeX, Linux}

\section{Professional Experience}
\cventry{Aug 2023 -- Present}{Data Scientist}{Acme Analytics Ltd.}{Springfield, Country}{}{
\begin{itemize}
  \item Developed and deployed an ML-based sales forecasting model, improving request planning accuracy by 15\% and reducing overstocks by 8\%.
  \item Automated ETL and reporting processes using Python and SQL, saving 10 hrs/week and enabling daily dashboard refresh.
  \item Designed customer segmentation analysis that supported targeted campaigns, yielding a 7\% engagement increase and a 3\% revenue lift.
\end{itemize}
}

\cventry{Jul 2022 -- Jul 2023}{Data Science Intern}{Acme Analytics Ltd.}{Springfield, Country}{}{
\begin{itemize}
  \item Built interactive Tableau dashboards for leadership, enabling daily KPI monitoring with auto-refresh.
  \item Led data preprocessing and feature engineering, reducing model iteration times by 20\% and improving reliability.
  \item Conducted exploratory analysis for new product lines, informing go-to-market strategies and priorities.
\end{itemize}
}

\section{Education}
\cventry{2020 -- 2022}{MSc in Data Science}{University of Springfield}{Springfield, Country}{\textit{Thesis:} ``ML Methods for Retail Demand Forecasting'' --- achieved 10\% MAE improvement over baseline models.}{}
\cventry{2016 -- 2020}{BSc in Computer Science}{University of Springfield}{Springfield, Country}{}{}

\section{Projects}
\cvitem{Sales-Forecaster Toolkit}{Built and open-sourced a PyTorch-based demand forecasting pipeline; over 500 downloads; achieved \textasciitilde 10\% MAE improvement vs baseline.}
\cvitem{Kaggle Churn Predictor}{Top 10\% finish in churn prediction challenge using ensemble techniques---ROC-AUC improved from 0.78 to 0.85.}

\section{Languages}
\cvitem{English}{C2 (native-level fluency)}
\cvitem{German}{B1 (intermediate working proficiency)}
\cvitem{French}{A2 (basic conversational)}

\end{document}
